---
title: "Using RevBayes in R"
author: "Caleb Charpentier and April Wright"
date: Sys.Date()
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using RevBayes in R}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


# Installation

Revticulate can be installed in two ways.
The first is via CRAN, using the default `install.packages` function in R:


```{r eval=FALSE}
install.packages("Revticulate")
```

The second is via the remotes package, a lightweight package enabling installation from GitHub repositories.


```{r}
remotes::install_github("revbayes/Revticulate")
```

The GitHub repository for Revticulate contains cutting-edge features and may contain bugfixes, but the CRAN is known to be stable for everyday use.

Upon first installation, Revticulate will run a package check.
This check searches for and `.Renviron` file that contains a RevBayes path. If the package doesn’t find this file, or finds it without the path, the package prompts the user to use `usethis::edit_r_environ()`. This opens the .Renviron file, and the user will enter `rb=/absolute/path/to/revbayes`. This can be edited at any time if there are multiple installs on the system, or if you recompile RevBayes and want to use a new version.

Before using Revticulate in knitr, make sure the following is in your setup chunk:

```{r}
library(Revticulate)
knitRev()
```

First, we will test that RevBayes is accessible to us. This is a Rev chunk, which we know because the header says 'rb'. This will fail if RevBayes cannot be found. If this is the case, check that the path in your `.Renviron` goes to RevBayes, and restart.

```{rb}
variable <- "Hi there! Welcome to RevBayes! I am now going to read in some test data."
variable
```

Next, we will attempt to read in some data. Note that this file is stored in `tutorial_structure/scripts`, and so we'll going up one directory to the data directory.

```{rb}
molecular_data <- readDiscreteCharacterData("../data/example_file.nex")
```
